---
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output: 
  html_document:
    toc:             false
    toc_float:       true
    number_sections: true
    code_folding:    hide
    df_print:        kable
    embed-resources: true
    
params:
  use_title: 'View Baseline Comparsion'

title: "`r params$use_title`"
---

# Workspace setup
```{r include=FALSE}
#| label: workspace
#| warning: false
#| message: false

here::i_am('B_script/data_quality_check_report.Rmd')
knitr::opts_chunk$set(warning   = F)
knitr::opts_chunk$set(message   = F)
knitr::opts_chunk$set(fig.align = 'center')
knitr::opts_chunk$set(dpi       = 200)
# knitr::opts_chunk$set(echo = TRUE)

sapply(
  c(
    'tidyverse',
    'magrittr',
    'lubridate',
    'gt'
  ),
  require,
  character.only = T
)

interactive_tbl <- function(tbl, use_filter = T, n = 20, active = F) {
  
  gt::gt(tbl) %>% 
    tab_style(
      style = cell_text(whitespace = 'break-spaces'),
      locations =
        cells_body(
          columns = where(is.character)
        )
    ) %>% 
    gt::opt_interactive(
      active            = active, 
      use_filters       = use_filter,
      use_compact_mode  = T,
      page_size_default = n
  )
  
}

```

# Summary

## Comparison groups
```{r}
#| label: summary-groupings

compare_groups %>% 
  arrange(group) %>% 
  pivot_wider(
    names_from  = group, 
    values_from = run_dt_tm
  ) %>% 
  knitr::kable()
```

# Columns and column values checks

## Views with missing or new columns
```{r}
#| label: col-check

df_metrics %>% 
  filter(!map_lgl(col_check, is.null)) %>% 
  {
    
    if (nrow(.) == 0) {
      
      cat('No missing or new cols')
      
    } else {
      
    pull(., col_check) %>% 
      bind_rows() %>% 
      gt() %>% 
      tab_style(
        style = cell_fill((color = alpha('salmon', 0.5))),
        locations =
          cells_body(
            columns = baseline,
            rows    = baseline == 'missing'
          )
      ) %>% 
      tab_style(
        style = cell_fill((color = alpha('salmon', 0.5))),
        locations =
          cells_body(
            columns = test,
            rows    = test == 'missing'
          )
      )
      
    }
    
  }

```

## Views with non-`float` columns containing missing or new values
```{r}
#| label: val-check

knit_val_chk <-
  df_metrics %>% 
  select(row, view, col, val_check) %>% 
  filter(!map_lgl(val_check, is.null)) %T>% 
  {
    
    tbl_val_chk <<-
      group_by(., view) %>% 
      summarise(n_cols = n()) %>% 
      mutate(
        link = 
          sprintf(
            '[link](#val_chk_%s)',
            view
          )
      )
    
  } %>% 
  split(.$view) %>% 
  map(
    ~ {
      
      df_by_view <- .x
      
      tbl_summary <-
        mutate(
          df_by_view,
          .keep = 'none',
          view = view, col = col,
          n_val_issues = map_int(val_check, nrow)
        ) %>% 
          knitr::kable() %>% 
          paste(collapse = '\n') %>%
          paste(
            '#### Summary',
            .,
            sep = '\n'
          )
      
      pmap(
        df_by_view,
        \(row, view, col, val_check) {
          
          knitr::knit_expand(
            text =
              paste(
                '#### {{ col }}',
                '``` {r}',
                '#| label: val-chk-[{{ view }}].[{{ col }}]',
                "
                df_metrics %>%
                  filter(
                    .data$row == '{{ row }}',
                  ) %>%
                  pluck('val_check', 1) %>% 
                  gt() %>% 
                  tab_style(
                    style = cell_text(whitespace = 'break-spaces'),
                    locations =
                      cells_body(
                        columns = where(is.character)
                      )
                  ) %>% 
                  tab_style(
                    style = cell_fill(color = alpha('salmon', 0.5)),
                    locations = 
                      cells_body(
                        columns = status,
                        rows    = status == 'missing'
                      )
                  )
                ",
                  
                '```',
                sep = '\n'
              )
          )
          
        }
      ) %>% 
        paste(collapse = '\n\n') %>% 
        paste(tbl_summary, ., sep = '\n\n') %>% 
        paste(
          sprintf(
            '### %s {.tabset #%s}', 
            unique(df_by_view$view),
            paste0('val_chk_', unique(df_by_view$view))
          ),
          ., sep = '\n\n'
        )
      
    }
  ) %>% 
  paste(collapse = '\n\n')

tbl_val_chk %>% 
  knitr::kable()

```

`r knitr::knit(text = knit_val_chk)`

# Counts

## High level view record counts
```{r}
#| label: view-row-counts

df_metrics %>% 
  filter(type != 'float') %>% 
  # pluck('df_compare', 1)
  mutate(
    .keep = 'none',
    view = view, col = col, type = type,
    n = 
      map(
        df_compare, 
        ~ list(.x$n_baseline, .x$n_test) %>% 
          map(sum, na.rm = T) %>% 
          set_names(c('baseline', 'test'))
      )
  ) %>% 
  unnest_wider(n) %>% 
  mutate(diff = test - baseline) %>% 
  count(view, baseline, test, diff) %>% 
  group_by(view) %>% 
  filter(diff >= 0 & n == max(na.rm = T, n)) %>%
  # filter(diff < 0) %>% 
  ungroup() %>% 
  select(-n) %>% 
  gt() %>% 
  cols_align(align = 'right', where(is.character)) %>% 
  fmt_number(
    columns = c(baseline, test),
    use_seps = T,
    drop_trailing_zeros = T
  ) %>% 
  tab_style(
    style = cell_fill(color = alpha('turquoise', 0.5)),
    locations =
      cells_body(
        columns = diff,
        rows    = diff >= 0
      )
  ) %>% 
  tab_style(
    style = cell_fill(color = alpha('salmon', 0.5)),
    locations =
      cells_body(
        columns = diff,
        rows    = diff < 0
      )
  )

```

## Views with non-`float` columns containing count differences
```{r}
#| label: col-val-counts

knit_counts <- 
  df_metrics %>% 
  filter(type != 'float') %>% 
  filter(map_lgl(col_check, is.null)) %>% 
  select(
    row, view, col, type, df_compare
  ) %>%
  mutate(
    df_compare =
      map(df_compare, ~ filter(.x, diff != 0))
  ) %>% 
  filter(map_lgl(df_compare, ~ nrow(.x) != 0)) %T>% 
  {
    
    tbl_counts <<-
      group_by(., view) %>%
      summarise(n_cols = n()) %>%
      mutate(
        link =
          sprintf(
            '[link](#cnt_%s)',
            view
          )
      )
      
      # mutate(
      #   ., 
      #   .keep = 'none',
      #   view = view, col = col, type = type,
      #   n_vals_with_diff_count = map_int(df_compare, nrow),
      #   link =
      #     sprintf(
      #       '[link](#cnt_%s)', paste(view, col, collapse = '_')
      #     )
      # )
    
  } %>% 
  split(.$view) %>% 
  map(
    ~ {
      
      df_by_view <- .x
      
      tbl_summary <-
        mutate(
          df_by_view,
          .keep = 'none',
          view = view, col = col,
          n_col_issues = map_int(df_compare, nrow)
        ) %>% 
          knitr::kable() %>% 
          paste(collapse = '\n') %>%
          paste(
            '#### Summary',
            .,
            sep = '\n'
          )
      
      pmap(
        df_by_view,
        \(row, view, col, type, df_compare) {
          
          knitr::knit_expand(
            text =
              paste(
                '#### {{ col }}',
                '``` {r}',
                '#| label: col_cnt-[{{ view }}].[{{ col }}]',
                "
                df_metrics %>%
                  filter(
                    .data$row == '{{ row }}',
                  ) %>%
                  pluck('df_compare', 1) %>% 
                  filter(.data$diff != 0) %>% 
                  gt() %>% 
                  tab_style(
                    style = cell_text(whitespace = 'break-spaces'),
                    locations =
                      cells_body(
                        columns = where(is.character)
                      )
                  )
                ",
                  
                '```',
                sep = '\n'
              )
          )
          
        }
      ) %>% 
        paste(collapse = '\n\n') %>% 
        paste(tbl_summary, ., sep = '\n\n') %>% 
        paste(
          sprintf(
            '### %s {.tabset #%s}', 
            unique(df_by_view$view),
            paste0('cnt_', unique(df_by_view$view))
          ),
          ., sep = '\n\n'
        )
      
    }
  ) %>% 
  paste(collapse = '\n\n')

tbl_counts %>% 
  knitr::kable()


```

`r knitr::knit(text = knit_counts)`

## Testing for distribution changes

-  only for columns with more than one level
-  only for columns with differences in the counts of the levels

```{r}
#| label: stats-test

alpha <- 0.05
df_metrics %>% 
  filter(type != 'float') %>% 
  select(row, view, col, type, df_compare) %>% 
  filter(map_lgl(df_compare, ~ any(.x$diff != 0))) %>% 
  filter(map_lgl(df_compare, ~ nrow(.x) != 1)) %T>% 
  {
    
    tbl_counts <<-
      group_by(., view) %>%
      summarise(n_cols = n()) %>%
      mutate(
        link =
          sprintf(
            '[link](#cnt_%s)',
            view
          )
      )
    
  } %>% 
  split(.$view) %>% 
  map(
    ~ {
      
      df_by_view <- .x
      browser()
      
      df_by_view %>% 
        pmap(
          \(row, view, col, type, df_compare) {
            
            browser('processing df_compare')
            
            #1 Chi-squared Test of independence first
            tbl_contingency <- 
              as.table(rbind(df_compare$n_baseline, df_compare$n_test))
            
            test_overall <- chisq.test(tbl_contingency)
            
            #1.1 If CST fails assumption, use Fisher's Exact Test
            fet_check <- 
              sum(test_overall$expected < 5) / length(test_overall$expected) > 0.2 ||
              any(test_overall$expected < 1)
            
            if (fet_check) { test_overall <- fisher.test(tbl_contingency) }
            
            #2 if col's overall change is significant, proceed to post-hoc
            if (test_overall$p.value < alpha) {
              
              #2.1 Standardized Residual Analysis
              df_compare[
              ]
              
                abs(test_overall$stdres) > case_match(alpha, 0.05 ~ 2, 0.001 ~ 3)
                df_compare
              
            }
            
            
            
          }
        )
      
    }
  )

```

